Online Laterality Battery Pre-Processing - short version

### 2020-04-21 battery-preprocessing_v3_DB.Rmd
saving before modifying for new dataset

---
title: "Online Laterality Battery Pre-Processing - short version"
author: "Adam Parker + Dorothy Bishop"
date: "1st Feb 2020"
output: html_document
---

>>>>

---
title: "Online Laterality Battery Pre-Processing - short version"
author: "Adam Parker + Dorothy Bishop"
date: "original version from 1st Feb 2020"
output: html_document
---
